A Taxonomy of Twists of Supersymmetric Yang--Mills Theory

### 2020-01-28 paper.tex
merge

\begin{definition}
The \emph{Chevalley-Eilenberg complex} for the Lie algebra $\gg$, with coefficients in $\oloc(\cE)$, will be defined as follows.  Consider the graded vector space
\[C^\bullet(\fg, \oloc(\cE)) = \bigoplus_n \hom(\wedge^n \fg, \oloc(\cE))[-n]\]
\brian{not crazy about the notation $C^\bu(\fg, \oloc(\cE))$ for just the graded vector space before knowing that $\oloc$ is a module.}
parametrizing multilinear maps $f\colon \fg^{\otimes n}\rightarrow \oloc(\cE)$ which satisfy the antisymmetry property
\[f(x_1, \dots, x_i, x_{i+1}, \dots, x_n) = (-1)^{|x_1||x_2|+1} f(x_1, \dots, x_{i+1}, x_i, \dots, x_n)\]
where $x_j \in \fg$.  The Chevalley-Eilenberg differential is given, following the sign conventions of \cite{SafronovCoisoInt}, by the formula
\[(\d_{\mr{CE}} f)(x_1, \dots, x_n) = \sum_{i < j}(-1)^{|x_i| \sum_{p=1}^{i-1} |x_p| + |x_j| \sum_{p=1,p\neq i}^{j-1} |x_p| +i+j+|f|} f([x_i, x_j], x_1, \dots, \widehat{x}_i, \dots, \widehat{x}_j, \dots, x_n).\]
The complex is additionally equipped with a degree $+1$ BV bracket via the formula
\[\{f, g\}(x_1, \dots, x_{k+l}) = \sum_{\sigma\in S_{k, l}} \mathrm{sgn}(\sigma) (-1)^{\epsilon+\epsilon_1} \{f(x_{\sigma(1)}, \dots, x_{\sigma(k)}), g(x_{\sigma(k+1)}, \dots, x_{\sigma(k+l)})\},\]
where $S_{k, l}$ is the set of $(k, l)$-shuffles, $\epsilon$ is the usual Koszul sign and
\[\epsilon_1 = |g|k + \sum_{i=1}^k |x_{\sigma(i)}|(l+|g|).\]
\end{definition}

@@

\begin{definition}
\label{infinitesimal_action_def}
Let $(E, Q_{\mr{BV}},\omega, I)$ be a classical field theory. 
\begin{itemize}
\item[(1)]
An \defterm{action} of a super Lie algebra $\fg$ on $(E, Q_{\mr{BV}}, \omega, I)$ is an element of cohomological degree zero 
\[I_\fg = \sum_{k\geq 0} I_{\fg}^{(k)} \text{ in } C^\bullet(\fg, \oloc(\cE)),\]
where $I_\fg^{(k)}$ is a multilinear map $\fg^{\otimes k} \to \oloc(\cE)$, that satisfies the following three conditions:
\begin{itemize}
\item[(a)] $I_\fg^{(0)} = I$.
\item[(b)] For each $k \geq 1$ and $x_1, \ldots, x_k \in \fg$ the local functional $I^{(k)}_\fg (x_1,\ldots, x_k)$ is at least quadratic in the fields.
\item[(c)] $I_\fg$ satisfies the Maurer--Cartan equation:
\[(\d_{\mr{CE}} + Q_{\mr{BV}}) I_\fg + \frac{1}{2} \{I_\fg, I_\fg\} = 0.\]
\end{itemize}
\item[(2)]
For each $k \geq 1$ there is a decomposition $I_\fg^{(k)} = \sum_{\ell} I_\fg^{(k),\ell}$ where $ I_\fg^{(k),\ell}(x_1,\ldots,x_k) \in \oloc(\cE)$ is $\ell$-linear in the fields $\cE$ for all $x_1,\ldots,x_k \in \fg$.
An action $I_\fg$ is called \defterm{elliptic} if the induced linear differential operator
\[
Q_{\mr{BV}} + \sum_{k \geq 1} \{I_\fg^{(k),2}, -\}
\]
is elliptic as a $C^\bu(\fg)$-linear differential operator.
\end{itemize}
\end{definition}

\begin{remark}
\brian{Explain $C^\bu(\fg)$-linear elliptic}
\end{remark}

@@

\begin{prop}
The functionals $I^{(1)}$ and $I^{(2)}$ (see \eqref{eq:gaugeI1} and \eqref{eq:gaugeI2}) in terms of the fields of 8d $\cN=1$ super Yang--Mills are
\begin{align*}
I^{(1)}(Q_t) &= \int \dvol\left(-(\rho, A_{1, 0}^*) - t(C, A_{0, 1}^*) - (\wt \chi + t\chi)\wt \phi^*\right) \\
&+ \int\dvol\left((F_{0, 2}, B^*) + t\Omega^{-1} F_{2, 0}\wedge B^* + (\ol\dd_{A_{0, 1}}\phi, C^*) + (t\dd_{A_{1, 0}} \phi, \rho^*) + \frac{1}{2}\Lambda F_{1, 1}(\chi^* - t\wt\chi^*)\right) \\
I^{(2)}(Q_t, Q_t) &= \int \dvol \left(t\chi^*\wt \chi^* + \frac{t}{2}\Omega^{-1}B^*\wedge B^* -\frac{1}{4}(\chi^* + t\wt\chi^*)^2 + t\phi c^*\right).
\end{align*}
\end{prop}

@@

We use the same twisting homomorphism $\phi\colon \MU(2) \to \Spin(6;\CC)$ and twisting data $\alpha\colon U(1) \to G_R$ as in Section \ref{sect:4d4holomorphictwist}.
Then, $S_+ \otimes W$ decomposes under $\MU(2)$ as
\[
S_+\otimes W\cong L\oplus L^*\oplus \det(L)\oplus \CC \cdot Q_0 \oplus \CC \oplus \det(L)^{-1}.
\]
Further, the representation $S_- \otimes W^*$ decomposes as
\[
S_+ \otimes W^* = L \oplus L^* \oplus \CC Q'\oplus\eend_0(L),
\]
where $\eend_0(L)\subset \eend(L)$ is the subspace of traceless endomorphisms. The supercharge $Q_0$ has rank $(1, 0)$ and the supercharge $Q'$ has rank $(0, 2)$. Moreover, both are square-zero and commute with each other. Therefore, we may consider a family of square-zero supercharges
\begin{equation}
Q_t = Q_0 + tQ'
\label{eq:4d412Hodgefamily}
\end{equation}
which is of rank $(1, 0)$ at $t=0$ and of rank $(1, 2)$ at $t\neq 0$.

>>>>

\begin{definition}
The \emph{Chevalley-Eilenberg complex} for the Lie algebra $\gg$, with coefficients in $\oloc(\cE)$, will be defined as follows.  Consider the graded vector space
\[C^\bullet(\fg, \oloc(\cE)) = \bigoplus_n \hom(\wedge^n \fg, \oloc(\cE))[-n]\]
parametrizing multilinear maps $f\colon \fg^{\otimes n}\rightarrow \oloc(\cE)$ which satisfy the antisymmetry property
\[f(x_1, \dots, x_i, x_{i+1}, \dots, x_n) = (-1)^{|x_1||x_2|+1} f(x_1, \dots, x_{i+1}, x_i, \dots, x_n)\]
where $x_j \in \fg$.  The Chevalley-Eilenberg differential is given, following the sign conventions of \cite{SafronovCoisoInt}, by the formula
\[(\d_{\mr{CE}} f)(x_1, \dots, x_n) = \sum_{i < j}(-1)^{|x_i| \sum_{p=1}^{i-1} |x_p| + |x_j| \sum_{p=1,p\neq i}^{j-1} |x_p| +i+j+|f|} f([x_i, x_j], x_1, \dots, \widehat{x}_i, \dots, \widehat{x}_j, \dots, x_n).\]
The complex is additionally equipped with a degree $+1$ BV bracket via the formula
\[\{f, g\}(x_1, \dots, x_{k+l}) = \sum_{\sigma\in S_{k, l}} \mathrm{sgn}(\sigma) (-1)^{\epsilon+\epsilon_1} \{f(x_{\sigma(1)}, \dots, x_{\sigma(k)}), g(x_{\sigma(k+1)}, \dots, x_{\sigma(k+l)})\},\]
where $S_{k, l}$ is the set of $(k, l)$-shuffles, $\epsilon$ is the usual Koszul sign and
\[\epsilon_1 = |g|k + \sum_{i=1}^k |x_{\sigma(i)}|(l+|g|).\]
\end{definition}

@@

\begin{definition}
\label{infinitesimal_action_def}
Let $(E, Q_{\mr{BV}},\omega, I)$ be a classical field theory. 
%\begin{itemize}
%\item[(1)]
An \defterm{action} of a super Lie algebra $\fg$ on $(E, Q_{\mr{BV}}, \omega, I)$ is an element of cohomological degree zero 
\[I_\fg = \sum_{k\geq 0} I_{\fg}^{(k)} \text{ in } C^\bullet(\fg, \oloc(\cE)),\]
where $I_\fg^{(k)}$ is a multilinear map $\fg^{\otimes k} \to \oloc(\cE)$, that satisfies the following three conditions:
\begin{itemize}
\item[(a)] $I_\fg^{(0)} = I$.
\item[(b)] For each $k \geq 1$ and $x_1, \ldots, x_k \in \fg$ the local functional $I^{(k)}_\fg (x_1,\ldots, x_k)$ is at least quadratic in the fields.
\item[(c)] $I_\fg$ satisfies the Maurer--Cartan equation:
\[(\d_{\mr{CE}} + Q_{\mr{BV}}) I_\fg + \frac{1}{2} \{I_\fg, I_\fg\} = 0.\]
\end{itemize}
%\item[(2)]
%For each $k \geq 1$ there is a decomposition $I_\fg^{(k)} = \sum_{\ell} I_\fg^{(k),\ell}$ where $ I_\fg^{(k),\ell}(x_1,\ldots,x_k) \in \oloc(\cE)$ is $\ell$-linear in the fields $\cE$ for all $x_1,\ldots,x_k \in \fg$.
%An action $I_\fg$ is called \defterm{elliptic} if the induced linear differential operator
%\[
%Q_{\mr{BV}} + \sum_{k \geq 1} \{I_\fg^{(k),2}, -\}
%\]
%is elliptic as a $C^\bu(\fg)$-linear differential operator.
%\end{itemize}
\end{definition}

@@

\begin{prop}
The functionals $I^{(1)}$ and $I^{(2)}$ (see \eqref{eq:gaugeI1} and \eqref{eq:gaugeI2}) in terms of the fields of 8d $\cN=1$ super Yang--Mills are
\begin{align*}
I^{(1)}(Q_t) &= \int \dvol\left(-(\rho, A_{1, 0}^*) - t(C, A_{0, 1}^*) - (\wt \chi + t\chi)\wt \phi^*\right) \\
&+ \int\dvol\left((F_{0, 2}, B^*) + t\Omega^{-1} F_{2, 0}\wedge B^* + (\ol\dd_{A_{0, 1}}\phi, C^*) + (t\dd_{A_{1, 0}} \phi, \rho^*) + \frac{1}{2}\Lambda F_{1, 1}(\chi^* - t\wt\chi^*) + \frac{1}{2}[\phi, \wt\phi](\chi^*+t\wt\chi^*)\right) \\
I^{(2)}(Q_t, Q_t) &= \int \dvol \left(t\chi^*\wt \chi^* + \frac{t}{2}\Omega^{-1}B^*\wedge B^* -\frac{1}{4}(\chi^* + t\wt\chi^*)^2 + t\phi c^*\right).
\end{align*}
\end{prop}

@@

We use the same twisting homomorphism $\phi\colon \MU(2) \to \Spin(6;\CC)$ and twisting data $\alpha\colon U(1) \to G_R$ as in Section \ref{sect:4d4holomorphictwist}.
Then, $S_+ \otimes W$ decomposes under $\MU(2)$ as
\[
S_+\otimes W\cong L\oplus L^*\oplus \det(L)\oplus \CC \cdot Q_0 \oplus \CC \oplus \det(L)^{-1}.
\]
Further, the representation $S_- \otimes W^*$ decomposes as
\[
S_- \otimes W^* = L \oplus L^* \oplus \CC Q'\oplus\eend_0(L),
\]
where $\eend_0(L)\subset \eend(L)$ is the subspace of traceless endomorphisms. The supercharge $Q_0$ has rank $(1, 0)$ and the supercharge $Q'$ has rank $(0, 2)$. Moreover, both are square-zero and commute with each other. Therefore, we may consider a family of square-zero supercharges
\begin{equation}
Q_t = Q_0 + tQ'
\label{eq:4d412Hodgefamily}
\end{equation}
which is of rank $(1, 0)$ at $t=0$ and of rank $(1, 2)$ at $t\neq 0$.
